Supplementary Methods for\\ \emph{Effectiveness of UNAIDS targets and HIV vaccination across 127 countries}

### 2016-10-20 Documents/supplementary_information.tex
More tweaks.

\usepackage{xr}
\externaldocument{extended_data_fig_1}
\externaldocument{extended_data_fig_2}

@@

Our model has 8 HIV states (\autoref{model_diag}): susceptible to HIV
infection ($S$ is the number of people susceptible), vaccinated
against HIV ($R$), acute HIV infection ($A$), undiagnosed HIV
infection ($U$), diagnosed but untreated HIV infection ($D$), treated
without viral suppression ($T$), viral suppression ($V$), and having
AIDS ($W$).  Viral suppression is defined as a viral load of less than
1000 viral RNA copies per mL of blood.  Viral suppression not only
extends survival but also dramatically reduces transmission
\autocite{vernazza2000, ioannidis2001, attia2009, May2014-gp}.
Transitions between model states are governed by a series of
differential equations parametrized using values found in other
studies, along with transmission rates derived from UNAIDS estimates
of incidence and prevalence (\autoref{model_param}).  The model is
deterministic, but uncertainty in the parameters is treated by running
the model 1000 times with samples from the parameter distributions
(\autoref{uncertainty}) and summarizing the model outcomes using the
median, 1st and 3rd quartiles (i.e., 25th and 75th percentiles), and
5th and 95th percentiles.  Each country was modeled separately
(\hyperref[effectiveness_Afghanistan]{Extended Data
  Figs.~\ref*{effectiveness_Afghanistan}}--\ref{effectiveness_Zimbabwe})
and the country simulations were aggregated to calculate global and
regional outcomes
(\hyperref[effectiveness_Global]{Extended Data
  Figs.~\ref*{effectiveness_Global}}--\ref{effectiveness_Western_Europe}).

\begin{figure}
  \centering
  \input{diagram}
  \caption{Model diagram.}
  \label{model_diag}
\end{figure}

>>>>

\usepackage{xr}
\externaldocument{extended_data_fig_1}
\externaldocument{extended_data_fig_2}
\externaldocument{extended_data_fig_3}

@@

Our model has 8 HIV states
(\hyperref[model_diag]{Extended Data Figs.~\ref*{model_diag}}):
susceptible to HIV infection ($S$ is the number of people
susceptible), vaccinated against HIV ($R$), acute HIV infection ($A$),
undiagnosed HIV infection ($U$), diagnosed but untreated HIV infection
($D$), treated without viral suppression ($T$), viral suppression
($V$), and having AIDS ($W$).  Viral suppression is defined as a viral
load of less than 1000 viral RNA copies per mL of blood.  Viral
suppression not only extends survival but also dramatically reduces
transmission
\autocite{vernazza2000, ioannidis2001, attia2009, May2014-gp}.
Transitions between model states are governed by a series of
differential equations parametrized using values found in other
studies, along with transmission rates derived from UNAIDS estimates
of incidence and prevalence (\autoref{model_param}).  The model is
deterministic, but uncertainty in the parameters is treated by running
the model 1000 times with samples from the parameter distributions
(\autoref{uncertainty}) and summarizing the model outcomes using the
median, 1st and 3rd quartiles (i.e., 25th and 75th percentiles), and
5th and 95th percentiles.  Each country was modeled separately
(\hyperref[effectiveness_Afghanistan]{Extended Data
  Figs.~\ref*{effectiveness_Afghanistan}}--\ref{effectiveness_Zimbabwe})
and the country simulations were aggregated to calculate global and
regional outcomes
(\hyperref[effectiveness_Global]{Extended Data
  Figs.~\ref*{effectiveness_Global}}--\ref{effectiveness_Western_Europe}).
